Test if analytic derivation of geodesic distance for curves from sim_functional_data.R

### 2019-06-26 test_analytic_geodesic_distance.Rmd
prepping compare_methods
fix problems in processRealData

use_python('/usr/local/bin/python3.7',required=TRUE)
# use_python('/Users/UQAM/anaconda3/bin/python',required=TRUE)
# use_python('/Users/suswei/anaconda3/bin/python',required=TRUE)

@@

Check with py_config()

@@

```{r}
# Generate data
sim <- sim_functional_data(sce=5,samplesize=200,K=30,plot_true=1,reg_sampling=1)
```

@@

Specifically, we would like to compare sim$analytic_geo to geodesic distance estimation via Floyd's algorithm for the noiseless (discretised) curve. This algorithm is guaranteed to do well if we sample the manifold densely enough? Setting the samplesize very high is not enough for this, a concentrated sampling of the manifold is actually needed. More on this in sim_functiona_data.R documentation. The number of grid points should not be too low since then the L2 distance between the discretized curves won't be well estimated. K=30 seems to suffice in general.

>>>>

# use_python('/usr/local/bin/python3.7',required=TRUE)
# use_python('/Users/UQAM/anaconda3/bin/python',required=TRUE)
# use_python('/Users/suswei/anaconda3/bin/python',required=TRUE)

@@

@@

```{r}
# Generate data
sim <- sim_functional_data(sce=2,samplesize=100,K=30,plot_true=1,reg_sampling=1)
```

@@

Specifically, we would like to compare sim$analytic_geo to geodesic distance estimation via Floyd's algorithm for the noiseless (discretised) curve. This algorithm is guaranteed to do well if we sample the manifold densely enough? Setting the samplesize very high is not enough for this, a concentrated sampling of the manifold is actually needed. More on this in sim_functiona_data.R documentation. The number of grid points should not be too low since then the L2 distance between the discretized curves won't be well estimated.
